DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox

### 2017-06-20 ase2017/paper.tex
reviewed paragraph about AA in the tool paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Control theory achieves the construction of reliable systems by 
offering mathematical guarantees about the stability and the desired 
performance of closed-loop systems, where states or outputs of discrete plant $G(z)$ 
are fed back and compared to a reference signal to which a (designed) 
controller $C(z)$ should maintain a set of control objectives~\cite{astrom1997computer}. 
Fig.~\ref{fig:typical-control-system} shows a typical closed-loop digital control system.
%
\begin{figure}[ht!]
\centering
\includegraphics[width=0.35\textwidth]{closedloopseries.pdf}
\caption{Typical Closed-loop Control System.}
\label{fig:typical-control-system}
\end{figure}

@@

Instead of unfolding the dynamics, the second approach shown in Figure~\ref{fig:CEGARIS}
employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to
evaluate all possible progressions of the system simultaneously. This eliminates the need for
a completenes threshold since the time horizon is always infinite.
Since this model is based on abstraction, we initially perform the synthesis over a basic
model that abstracts away the complexity of the specification and is only refined to a more
complex model when a counterexample is found. Thus we may only look at the gain of the
system to synthesise a controller and add further restrictions on specific sections of the reach
tube when these prove to invalidate the solution. The use of Counter-Example Guided 
Abstraction Refinement results in much faster synthesis and verification since it is applied to
both phases,allowing for faster results whilst maintaining soundness for an infinite time horizon.

>>>>

Control theory achieves the construction of reliable systems by 
offering mathematical guarantees about the stability and the desired 
performance of closed-loop systems, where states or outputs of discrete plant $G(z)$ 
are fed back and compared to a reference signal to which a (designed) 
controller $C(z)$ should maintain a set of control objectives~\cite{astrom1997computer}. 
Fig.~\ref{fig:typical-control-system} shows a typical closed-loop digital control system.
%
\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{closedloopseries.pdf}
\caption{Typical Closed-loop Control System.}
\label{fig:typical-control-system}
\end{figure}

@@

Instead of unfolding the dynamics, the second approach shown in Figure~\ref{fig:CEGARIS}
employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to
evaluate all possible progressions of the system simultaneously. This eliminates the need for
a completenes threshold since the time horizon is always infinite.
Since this model is based on abstraction, we initially perform the synthesis over a basic
model that abstracts away the complexity of the specification and is only refined to a more
complex model when a counterexample is found. Thus, we may only look at the gain of the
system to synthesise a controller and add further restrictions on specific sections of the reach
tube when these prove to invalidate the solution. The use of Counterexample-Guided 
Abstraction Refinement results in much faster synthesis and verification since it is applied to
both phases, allowing for faster results whilst maintaining soundness for an infinite time horizon.
